### 2019-01-04 taco/tex/intro.tex
Add TACO

{\color{blue}
Various efforts of performance optimization have been made among computing frameworks, both at the software and hardware levels \cite{sync, tachyon, heintz2016end, zhang2015prism, cheng2017improving, chen2017heterogeneous, yviquel2018cluster, kaitoua2014hadoop, wasi2017comprehensive}. However, the shuffle phase is often poorly optimized in practice.
}
% {\color{red}
% Although continuous efforts of performance optimization have been made among a variety of computing frameworks\cite{sync, babu, tachyon, pacman, quincy, delay, ibrahim2012maestro, sharma2012mrorchestrator}, 
% the shuffle is often poorly optimized in practice.
% }
% take over shuffle
%shuffle characteristic
In particular, we observe that one major deficiency lies in the lack of fine-grained, coordinated management among different system resources.
%In the current practice, the shuffle phase is often split into two parts --- \textit{shuffle read} and \textit{shuffle write}. 
As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stages (i.e., map task).  
And the \textit{shuffle read} fetches intermediate results from remote disks through network, which is commonly integrated as part of the tasks in descendant stages (i.e., reduce task). 
Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk, and network) named \textit{slot} is assigned to a task, and the resources are released only after the task finishes.
Such task aggregation together with the coarse-grained scheduling effectively simplifies task management.
However, since a cluster has a limited number of slots, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
%The map task in Figure \ref{fig:workflow} well explains such deficiency: the I/O resource allocated to the stage is always idle during the computation time, and the computation/memory resource is totally wasted during the shuffle write attached to it, and vice versa.

>>>>

{\color{blue}
Various efforts of performance optimization have been made among computing frameworks, both at the software and hardware levels \cite{sync, tachyon, heintz2016end, zhang2015prism, cheng2017improving, chen2017heterogeneous, yviquel2018cluster, kaitoua2014hadoop, wasi2017comprehensive, zhang2018simpo, chen2013tiled}. However, the shuffle phase is often poorly optimized in practice.
}
% {\color{red}
% Although continuous efforts of performance optimization have been made among a variety of computing frameworks\cite{sync, babu, tachyon, pacman, quincy, delay, ibrahim2012maestro, sharma2012mrorchestrator}, 
% the shuffle is often poorly optimized in practice.
% }
% take over shuffle
%shuffle characteristic
In particular, we observe that one major deficiency lies in the lack of fine-grained, coordinated management among different system resources.
%In the current practice, the shuffle phase is often split into two parts --- \textit{shuffle read} and \textit{shuffle write}. 
As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stages (i.e., map task).  
And the \textit{shuffle read} fetches intermediate results from remote disks through network, which is commonly integrated as part of the tasks in descendant stages (i.e., reduce task). 
Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk, and network) named \textit{slot} is assigned to a task, and the resources are released only after the task finishes.
Such task aggregation together with the coarse-grained scheduling effectively simplifies task management.
However, since a cluster has a limited number of slots, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
%The map task in Figure \ref{fig:workflow} well explains such deficiency: the I/O resource allocated to the stage is always idle during the computation time, and the computation/memory resource is totally wasted during the shuffle write attached to it, and vice versa.
